Improvement of crash forces in structures using optimization tools.

### 2016-07-27 paper.tex
Avances

\documentclass[cmfonts]{witpress}
\usepackage{todonotes}
\usepackage{siunitx}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{cleveref}
\usepackage{amssymb}
% \usepackage{natbib}
\bibliographystyle{witpress}

@@

@@

\begin{figure}[htpb]
	\centering
	\includegraphics[height=5cm]{figures/IMG_CUTRES/general_transp}
	\caption{General view of the model with the bounding box.}
	\label{fig:general}
\end{figure}

>>>>

\documentclass[cmfonts]{witpress}
\usepackage{todonotes}
\usepackage{siunitx}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{cleveref}
\usepackage{amssymb}
\usepackage{subcaption}
\captionsetup{compatibility=false}
% \usepackage{natbib}
\bibliographystyle{witpress}

@@

\begin{figure}[ht]
  \centering
  \begin{minipage}[b]{.48\linewidth}
    \centering
    \includegraphics[width=0.5\linewidth]{figures/IMG_CUTRES/medidas_cb}
    \subcaption{Dimensions of the modeled crash boxes, in millimeters. Taken from \cite{Peroni2009}.}
    \label{fig:crash_box}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{.48\linewidth}
    \centering
    \includegraphics[width=0.4\textwidth]{figures/IMG_CUTRES/general_transp}
    \subcaption{General view of the model with the bounding box.}
    \label{fig:general}
  \end{minipage}
  \caption{Dimensions of the studied crash boxes and view of the finite element model including a bounding box.}
  \label{fig:modelo}
\end{figure}

@@

\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.4\textwidth]{figures/IMG_CUTRES/general_transp}
	\caption{General view of the model with the bounding box.}
	\label{fig:general}
\end{figure}
